Coevolution leaves a stronger imprint on interactions than on community structure

### 2017-06-06 manuscript/manuscript.Rmd
revision 2

![Spatial distribution of co-phylogenetic matching across the 51 sites. For each location, we indicate whether or not the structure of regional and local interaction networks is consistent with phylogenetic congruence. Locations where the local network shows a significant co-phylogenetic structure are marked with triangles. Locaitions where the regional network shows a significant co-phylogenetic structure are in black. See also {@tbl:contingency}. ](figure/maps-1.pdf){#fig:maps width=100%}

@@

Beyond their contribution to co-phylogenetic matching, interactions also
ultimately differ in how frequently they vary when the species involved co-occur
[@olit15staa; @troj15gvm; @cars14bdp]. This can happen, for example, when one of
the partners is able to forage for optimal resources [@bett15prk]. Once more,
the literature on host-parasite interactions assumes that the reason why some
interactions are more frequent is because they reflect a significant past
history of coevolution [@guim07iia; @mora10bhi]; that is, the ecological
constraints emerge from evolutionary conservatism. Using a weighted Pearson's
correlation between the interaction frequency, interaction contribution to
co-phylogenetic matching, and the number of observations of each interaction as
the weight, we observe that this is marginally true ($\rho \approx -0.11$. $t
\approx -5.09$ with weights; $\rho \approx -0.10$, $t \approx -4.6$ without;
both significant at $\alpha = 0.05$; {@fig:consistency}). Recall that the
*negative* correlation here arises from the fact that high interaction-level
values in PACo means *low* contribution to co-phylogenetic signal. Nevertheless,
the significance of this result ought to be tempered by the fact that the $R^2$
of both regressions is close to $0.01$. Consequently, the association between
spatial consistency and contribution to co-phylogenetic signal, while
statistically significant, explains so little variance of either quantities that
it is likely of negligible biological importance. This implies that the spatial
consistency of an interaction does not necessarily reflect its evolutionary
past, but rather (possibly) extant ecological processes.

@@

Local networks show little to no signal of co-phylogenetic matching, and the
strength of co-phylogenetic matching that can be ascribed to the interactions
between two species is a surprisingly poor predictor of how frequently they
interact. In contrast to the frequent assumption that phylogenetic structure is
a key driver of community structure [@cave09mce], these data reveal that this
impact is actually minimal at ecologically relevant spatial scales, even in
a system where phylogenetic structure would be expected to have a profoundly
strong role. And yet, despite all the above, individual interactions are somehow
able to maintain their co-phylogenetic matching even when the community they are
woven into does not. Thinking more broadly, these discrepancies provide a
roadmap for bridging the gap between our appreciation of the role of shared
evolutionary history and its empirically measurable outcomes: network structure
is the most parsimonious *mechanism* by which coevolution proceeds, not the
imprint potential coevolution leaves on ecological communities.

>>>>

![Spatial distribution of co-phylogenetic matching across the 51 sites. For each location, we indicate whether or not the structure of regional and local interaction networks is consistent with phylogenetic congruence. Locations where the local network shows a significant co-phylogenetic structure are marked with triangles. Locaitions where the regional network shows a significant co-phylogenetic structure are in black.](figure/maps-1.pdf){#fig:maps width=100%}

@@

Beyond their contribution to co-phylogenetic matching, interactions also
ultimately differ in how frequently they vary when the species involved co-occur
[@olit15staa; @troj15gvm; @cars14bdp]. This can happen, for example, when one of
the partners is able to forage for optimal resources [@bett15prk]. Once more,
the literature on host-parasite interactions assumes that the reason why some
interactions are more frequent is because they reflect a significant past
history of coevolution [@guim07iia; @nieb10ucp]; that is, the ecological
constraints emerge from evolutionary conservatism. Using a weighted Pearson's
correlation between the interaction frequency, interaction contribution to
co-phylogenetic matching, and the number of observations of each interaction as
the weight, we observe that this is marginally true ($\rho \approx -0.11$. $t
\approx -5.09$ with weights; $\rho \approx -0.10$, $t \approx -4.6$ without;
both significant at $\alpha = 0.05$; {@fig:consistency}). Recall that the
*negative* correlation here arises from the fact that high interaction-level
values in PACo means *low* contribution to co-phylogenetic signal. Nevertheless,
the significance of this result ought to be tempered by the fact that the $R^2$
of both regressions is close to $0.01$. Consequently, the association between
spatial consistency and contribution to co-phylogenetic signal, while
statistically significant, explains so little variance of either quantities that
it is likely of negligible biological importance. This implies that the spatial
consistency of an interaction does not necessarily reflect its evolutionary
past, but rather (possibly) extant ecological processes.

@@

Local networks show little to no signal of co-phylogenetic matching, and the
strength of co-phylogenetic matching that can be ascribed to the interactions
between two species is a surprisingly poor predictor of how frequently they
interact. In contrast to the frequent assumption that phylogenetic structure is
a key driver of community structure [@cave09mce], these data reveal that this
impact is actually minimal at ecologically relevant spatial scales, even in a
system where phylogenetic structure would be expected to have a profoundly
strong role. And yet, despite all the above, individual interactions are somehow
able to maintain their co-phylogenetic matching even when the community they are
woven into does not. Thinking more broadly, these discrepancies provide a
roadmap for bridging the gap between our appreciation of the role of shared
evolutionary history and its empirically measurable outcomes: network structure
is the most parsimonious *mechanism* by which coevolution proceeds, not the
imprint potential coevolution leaves on ecological communities [@poni17clw].
